\documentclass[14pt, aspectratio=1610]{beamer}
\usetheme{metropolis}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\setbeamertemplate{navigation symbols}{}
\definecolor{emphasis}{RGB}{0, 102, 204}

\title{CASE Tools}
\author{Amrit Bhattarai\thanks{Makes these types of slides.}\\Anupam Baral\thanks{Just presents.}}

\begin{document}

% Title slide
\maketitle

% First content frame
\begin{frame}{What are \textbf{CASE Tools}?}
	\begin{itemize}
		\item<1-> \textbf{CASE} stands for \textcolor{emphasis}{Computer-Aided Software Engineering}.
		\item<1-> \textbf{CASE Tools} help system analysts to:
			\begin{enumerate}
				\item<2-> Develop information systems.
				\item<2-> Maintain information systems.
			\end{enumerate}
		\item<3-> These tools aim to \textcolor{emphasis}{automate} the software development lifecycle.
	\end{itemize}
\end{frame}

% Second content frame
\begin{frame}{Types of CASE Tools}
	\begin{columns}

		\column{0.5\textwidth}
		\textbf{Upper CASE Tools} \pause
		\begin{itemize}
			\item Focus on planning and analysis phases. \pause
			\item Examples: Requirements gathering tools, modeling tools. \pause
		\end{itemize}

		\column{0.5\textwidth}
		\textbf{Lower CASE Tools} \pause
		\begin{itemize}
			\item Focus on implementation and testing phases. \pause
			\item Examples: Code generators, debuggers. \pause
		\end{itemize}

	\end{columns}
\end{frame}

% New slide: Features
\begin{frame}{Key Features of CASE Tools}
	\begin{itemize}
		\item<1-> Graphical user interfaces for system modeling. \pause
		\item<2-> Integration with version control systems. \pause
		\item<3-> Automatic code generation from models. \pause
		\item<4-> Support for documentation and report generation. \pause
		\item<5-> Traceability from requirements to code and tests. \pause
		\item<6-> Collaboration features for team development.
	\end{itemize}
\end{frame}

% New slide: Advantages
\begin{frame}{Advantages of CASE Tools}
	\begin{itemize}
		\item<1-> Increases productivity by automating routine tasks. \pause
		\item<2-> Improves software quality through standardization. \pause
		\item<3-> Enhances documentation and communication. \pause
		\item<4-> Reduces development time and cost. \pause
		\item<5-> Facilitates early detection of errors.
	\end{itemize}
\end{frame}

% New slide: Disadvantages
\begin{frame}{Disadvantages of CASE Tools}
	\begin{itemize}
		\item<1-> High initial cost of acquisition and training. \pause
		\item<2-> Steep learning curve for some tools. \pause
		\item<3-> Resistance to change from traditional methods. \pause
		\item<4-> May not fit all project types or sizes. \pause
		\item<5-> Dependency on tool support and updates.
	\end{itemize}
\end{frame}

% New slide: Conclusion
\begin{frame}{Conclusion}
	\begin{itemize}
		\item<1-> CASE tools play a critical role in modern software engineering. \pause
		\item<2-> When used appropriately, they can significantly improve development efficiency and quality. \pause
		\item<3-> However, careful evaluation is necessary before adoption.
	\end{itemize}
\end{frame}

\end{document}
